Comparison of Catalogs

### 2024-11-04 compare/compare.qmd
fixed outer join
- all2 -> 1or2
- updated the catalog

ax.errorbar(dt["TType"].data, dt["T"].data, yerr = dt["E_T"].data, fmt='none', capsize=2, zorder=1, color = "blue")
temp = dt[["TType", "T"]].to_pandas().dropna()
results = scipy.stats.linregress(x = temp["TType"],
                                y = temp["T"])
plt.xlabel("$Type_{LVG}$")
plt.ylabel("$Type_{HEC}$")
plt.legend(["Data",
            "$T_{HEC}=$" +f"{results.slope:.2f}"+"$\cdot T_{LVG}+$"+
            f"$({results.intercept:+.2f})$"+
            f"\n $R^2 = {results.rvalue**2*100:.0f}\%$"])
plt.show()

>>>>

ax.errorbar(dt["TType"].data, dt["T"].data, yerr = dt["E_T"].data, fmt='none', capsize=2, zorder=1, color = "blue")
temp = dt[["TType", "T"]].to_pandas().dropna()
temp["TType"] = temp["TType"].astype("float64")
temp["T"] = temp["T"].astype("float64")

results = scipy.stats.linregress(x = temp["TType"],
                                y = temp["T"])
plt.xlabel("$Type_{LVG}$")
plt.ylabel("$Type_{HEC}$")
plt.legend(["Data",
            "$T_{HEC}=$" +f"{results.slope:.2f}"+"$\cdot T_{LVG}+$"+
            f"$({results.intercept:+.2f})$"+
            f"\n $R^2 = {results.rvalue**2*100:.0f}\%$"])
plt.show()
